\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-02-04 Drafts and notes/Old_draft_05.tex
Added proof of rate of convergence for the simple case

%============%============%============%============%
%\setlength{\columnseprule}{0.4pt}
%\setlength{\topmargin}{0cm}
%\setlength{\oddsidemargin}{.25cm}
%\setlength{\evensidemargin}{.25cm}
%\setlength{\textheight}{22.5cm}
%\setlength{\textwidth}{15.5cm}
\renewcommand{\baselinestretch}{1.05}
%============%============%============%============%
\usepackage[toc,page]{appendix}
%============%============%============%============%
\usepackage{xcolor}
\usepackage{placeins}
\usepackage{amsfonts,amsmath,amsthm}
\usepackage{amssymb,epsfig}
\usepackage{enumerate} 
\usepackage[notcite,notref]{showkeys}
\usepackage{fullpage}
%============%============%============%============%
\usepackage[utf8]{inputenc}
%\usepackage{mathpazo}
%\usepackage[euler-digits]{eulervm}
\usepackage[libertine,cmintegrals,cmbraces,vvarbb]{newtxmath}
\usepackage{eucal}
\usepackage[unicode=true]{hyperref}
\hypersetup{colorlinks = true}
%\hypersetup{hidelinks=true}
\hypersetup{
     colorlinks,
     linkcolor={black!10!red},
     linkbordercolor = {black!100!red},
%    <your other options...>,
     citecolor={blue}
}

@@

\section{Preliminaries}\label{sec:prelim}
\subsection{Gradient estimate}

@@

\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps}.
\end{thm}

\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$. 
\begin{figure}[ht]
    \centering
    %\incfig{Domains}
    \def\svgwidth{0.47\columnwidth}
    \import{./figs/}{Domains.pdf_tex}
    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
    \label{fig:Domains}
\end{figure}
We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region. We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that 
\begin{equation*}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
    \end{cases}
\end{equation*}
We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.

\noindent To find candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the ansatz
\begin{equation}\label{eq:ansatz}
    u(x) = C_0 d(x)^{-\alpha}, \qquad x\in \Omega
\end{equation}
as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$. Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that the highest order terms are
\begin{equation*}
        -C_0 \alpha(\alpha+1)d^{-(\alpha+2)} + C_0^p \alpha^p d^{-(\alpha+1)p}.
\end{equation*}
Setting them to zero, we deduce that
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_0 = \frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}.
\end{equation*}
We can obtain the following families of supersolution on $\Omega_\delta$ and subsolution on $\Omega^\delta$ as follow.
\begin{equation*}
        \overline{w}_{\eta,\delta}(x) = \frac{C_0+\eta}{(d(x)-\delta)^\alpha} +\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega_\delta \qquad\text{and}\qquad \underline{w}_{\eta,\delta}(x) = \frac{C_0-\eta}{(d(x)+\delta)^\alpha} -\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega^\delta.
\end{equation*}
We divide the rest of the proof into 3 steps. We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and uniqueness of solution to \eqref{eq:PDEeps}.

\begin{prop}\label{pro:minimalsol} There exists a minimal solution $\underline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\geq \underline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
\end{prop}
\begin{proof} Let $w_{\eta,\delta}\in \mathrm{C}^2(\Omega)$ solves
    \begin{equation}\label{e:w_def}
    \begin{cases}
        \mathcal{L}\left[w_{\eta,\delta}\right] = 0 &\qquad\text{in}\;\Omega,\\
        \qquad w_{\eta,\delta} = \underline{w}_{\eta,\delta} &\qquad\text{on}\;\partial\Omega.
    \end{cases}
    \end{equation}
    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\leq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.

@@

\section{Rate of convergence via Doubling variables}
\noindent Let $\Omega = B(0,1)$. Fix $\theta \in (0,1)$ to be chosen later, let us define
\begin{align*}
    \Psi^{\sigma}(x,y) = \theta u^\varepsilon(x) - u^0(y) - \frac{|x-y|^2}{\sigma}- \frac{C_0}{d(x)^\alpha}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega} 
\end{align*}
where $\sigma>0$ to be chosen later.

\section{Rate of convergence via a simple idea}
\noindent Let $\Omega = B(0,1)$, the scaling and distance near boundary are the same, i.e., $(1-\delta)\Omega = \Omega_\delta$.

>>>>

%============%============%============%============%
%\setlength{\columnseprule}{0.4pt}
%\setlength{\topmargin}{0cm}
%\setlength{\oddsidemargin}{.25cm}
%\setlength{\evensidemargin}{.25cm}
%\setlength{\textheight}{22.5cm}
%\setlength{\textwidth}{15.5cm}
\renewcommand{\baselinestretch}{1.05}
%============%============%============%============%
\usepackage[toc,page]{appendix}
%============%============%============%============%
\usepackage{xcolor}
\usepackage{placeins}
\usepackage{amsfonts,amsmath,amsthm}
\usepackage{amssymb,epsfig}
\usepackage{enumerate} 
\usepackage[notcite,notref]{showkeys}
\usepackage{fullpage}
%============%============%============%============%
\usepackage[utf8]{inputenc}
%\usepackage{mathpazo}

%\usepackage[libertine,cmintegrals,cmbraces,vvarbb]{newtxmath}
\usepackage{eucal}
\usepackage[euler-digits]{eulervm}
\usepackage[unicode=true]{hyperref}
\hypersetup{colorlinks = true}
%\hypersetup{hidelinks=true}
\hypersetup{
     colorlinks,
     linkcolor={black!10!red},
     linkbordercolor = {black!100!red},
%    <your other options...>,
     citecolor={blue}
}

@@

\section{Preliminaries}\label{sec:prelim} 
\subsection{Setting and simplifications} Let $\delta_0>0$ be a fixed number such that $\mathrm{dist}(x,\partial\Omega)$ is $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$, i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) < \delta_0$. We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that 
\begin{equation*}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_{\delta_0},\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^{\delta_0}\backslash \Omega.
    \end{cases}
\end{equation*}
Let us denote
\begin{equation*}
    K := \max_{x\in \overline{\Omega}} |\Delta d(x)|.
\end{equation*}
\noindent Let us denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC^2(\Omega)$ the operator
\begin{equation*}
    \mathcal{L}^\varepsilon[u](x) := \lambda u(x) + |Du(x)|^p - f(x) - \varepsilon \Delta u(x), \qquad x\in \Omega.
\end{equation*}
\subsection{Gradient estimate}

@@

\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that
\begin{equation*}
    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
\end{equation*}
where
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
\end{equation*}
\end{thm}

\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ $\textcolor{orange}{(\mathrm{dist}(x,\partial \Omega) > \delta)}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$. 
\begin{figure}[ht]
    \centering
    %\incfig{Domains}
    \def\svgwidth{0.47\columnwidth}
    \import{./figs/}{Domains.pdf_tex}
    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
    \label{fig:Domains}
\end{figure}
We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region. We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that 
\begin{equation*}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
    \end{cases}
\end{equation*}
We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.

\noindent To find a candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the \emph{ansatz}
\begin{equation}\label{eq:ansatz}
    u(x) = C_\varepsilon d(x)^{-\alpha}, \qquad x\in \Omega
\end{equation}
as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$. Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that 
\begin{align*}
    \lambda u(x) &\approx C_\varepsilon d(x)^{-\alpha},\\
    \frac{\partial u}{\partial x_i}(x) &\approx -\alpha C_\varepsilon d(x)^{-(\alpha+1)} \frac{\partial d}{\partial x_i}(x) \qquad\qquad\qquad \Longrightarrow\qquad |Du (x)|^p \approx \alpha^p C_\varepsilon^p d(x)^{-p(\alpha+1)}|\nabla d(x)|^p,\\
    %\frac{\partial^2 u}{\partial x_i^2}(x) &\approx \alpha(\alpha+1)C_0 d(x)^{-(\alpha+2)}\left|\frac{\partial d}{\partial x_i}(x)\right|^2 -\alpha C_0 d(x)^{-(\alpha+1)}\frac{\partial ^2 d}{\partial x_i^2}(x),\\
    \varepsilon\Delta u(x) &\approx \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|\nabla d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
\end{align*}
As $|\nabla d(x)| = 1$ for $x$ near $\partial\Omega$, we see that as $x\to \partial \Omega$, the highest explosive order terms are
\begin{equation*}
        -\varepsilon C_\varepsilon \alpha(\alpha+1)d^{-(\alpha+2)} + C_\varepsilon^p \alpha^p d^{-(\alpha+1)p}.
\end{equation*}
Setting them to zero, we deduce that
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
\end{equation*}
We can obtain the following families of supersolution on $\Omega_\delta$ and subsolution on $\Omega^\delta$ as follow. Let us denote
\begin{equation*}
    G = \left[\left(K\delta_0+(\alpha+1)\right)^\frac{1}{p-1} - (\alpha+1)^{\frac{1}{p-1}}\right]\alpha.
\end{equation*}

\begin{lem}\label{lem:subsln} For each $<\delta < \frac{1}{2}\delta_0$, if $\color{red}\eta\geq G\varepsilon^{\frac{1}{p-1}}$,\color{black} we have
\begin{equation*}
    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon+\eta}{(d(x)-\delta)^\alpha} +\frac{M}{\lambda},\qquad x\in \Omega_\delta
\end{equation*}
is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$ where
\begin{equation*}
    M = \max_{\overline{\Omega}} f(x) + 2^{\alpha+1}K\alpha\varepsilon\delta_0^{-(\alpha+1)}.
\end{equation*}
\end{lem}
\begin{proof} We compute
\begin{align*}
    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M_\eta + \frac{(C_\varepsilon+\eta)^p \alpha^p}{(d(x)-\delta)^{p(\alpha+1)}}|\nabla d(x)|^p - f(x) \\
    &\qquad\qquad\qquad\qquad\quad\;\,  - \frac{\varepsilon(C_\varepsilon+\eta)\alpha(\alpha+1)}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^2 + \frac{\varepsilon(C_\varepsilon+\eta)\alpha}{(d(x)-\delta)^{\alpha+1}}\Delta d(x).
\end{align*}
\textcolor{red}{to be filled in...}
\end{proof}

\begin{lem}\label{lem:supersln} For each $\eta>0$ there exists $M_\eta > 0$ such that 
\begin{equation*}
    \overline{w}_{\eta,\delta}(x) \textcolor{orange}{(\underline{w}_{\eta, \delta})} = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\eta}{\lambda}, \qquad x\in \Omega^\delta 
\end{equation*}
is a supersolution $\textcolor{orange}{(subsolution)}$ of \eqref{eq:PDEeps} in $\Omega^\delta$.
\end{lem}

We divide the rest of the proof into 3 steps. We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and uniqueness of solution to \eqref{eq:PDEeps}.

\begin{prop}\label{pro:minimalsol} There exists a minimal solution $\underline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\geq \underline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
\end{prop}
\begin{proof} Let $w_{\eta,\delta}\in \mathrm{C}^2(\Omega)$ solves
    \begin{equation}\label{e:w_def}
    \begin{cases}
        \mathcal{L}\left[w_{\eta,\delta}\right] = 0 &\qquad\text{in}\;\Omega,\\
        \qquad w_{\eta,\delta} = \underline{w}_{\eta,\delta} &\qquad\text{on}\;\partial\Omega.
    \end{cases}
    \end{equation}
    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\geq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.

@@

\section{Rate of convergence via Doubling variables - a toy case}
\noindent Let $\Omega = B(0,1)$. Let $\beta,\sigma,\delta \in (0,1)$ to be chosen later, let us define
\begin{align*}
    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{L_0|x-y|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta
\end{align*}
where $L_0$ is the Lipschitz constant of $u^0$ and $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ is the state-constraint solution to
\begin{equation*}
    \begin{cases}  
    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 \qquad\text{in}\; \Omega_\delta\\
    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 \qquad\text{on}\; \overline{\Omega}_\delta.
    \end{cases}
\end{equation*}
As we are working with the ball, note that $\Omega_\delta = (1-\delta)\Omega$. Let $\mathfrak{F}$ be the Lipschitz constant of $f$.
\paragraph{\textcolor{blue}{\textbf{Step 1.}}} Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}_\delta$ such that 
\begin{equation*}
    \max_{\overline{\Omega}\times \overline{\Omega}_\delta} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
\end{equation*}
\paragraph{\textcolor{blue}{\textbf{Step 2.}}} $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$ gives us that
    \begin{equation}\label{e:est_sigma2}
        \mathfrak{C}\frac{|x_\sigma-y_\sigma|^2}{\sigma} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq \mathfrak{C}|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.
    \end{equation}
    This gives us that
    \begin{equation}\label{e:est_sigma3}
        |x_\sigma|\leq |y_\sigma|+\sigma \qquad\Longrightarrow\qquad d(x_\sigma) \geq d(y_\sigma) - \sigma\geq \delta-\sigma.
    \end{equation}
Let 
\begin{equation*}
   \fbox{$\displaystyle \delta = 2\sigma$.}
\end{equation*}
then 
\begin{equation*}
    \fbox{$d(x_\sigma) \geq \sigma$.}
\end{equation*}
\paragraph{\textcolor{blue}{\textbf{Step 3.}}} $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, thus 
\begin{align*}
    &\lambda u^\varepsilon(x_\sigma) + \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma )\right|^p - f(x_\sigma)\\
    &\qquad\qquad\qquad -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|\nabla d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0.
\end{align*}
\paragraph{\textcolor{blue}{\textbf{Step 4.}}} $y\mapsto \Phi^\sigma(x_\sigma,y)$ has a maximum at $y_\sigma\in \overline{\Omega}$, thus 
\begin{equation*}
    \lambda u_\delta(y_\sigma) + \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma}\right|^p - f(y_\sigma) \geq 0
\end{equation*}
\paragraph{\textcolor{blue}{\textbf{Step 5.}}} Gradient estimate, let
\begin{equation*}
    \xi_\sigma = \frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma)
\end{equation*}
then $|\xi_\sigma|\leq 2\mathfrak{C}$ already and furthermore
\begin{equation*}
   \xi_\sigma+\zeta_\sigma \in D^-u^\varepsilon(x_\sigma),
\end{equation*}
which, by the local gradient estimate, as $x_\sigma\in \Omega_{\sigma}$, this is bounded in terms of $\sigma$ and will blow up as $\sigma\to 0$. Nevertheless, we can do better as following.
\begin{equation*}
 |\zeta_\sigma|=   \left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma )\right| \leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}}\leq \frac{\alpha+\beta}{\alpha} (\alpha+1)^\frac{1}{p-1}\frac{\varepsilon^\frac{1}{p-1}}{\sigma^{\alpha+\beta+1}}.
\end{equation*}
Thus by choosing $\sigma = \varepsilon^\gamma$ appropriately, we can make this tends to zero as $\varepsilon \to 0$. Indeed, we have
\begin{equation*}
    |\zeta_\sigma| \leq \frac{(\alpha+1)^\frac{1}{p-1}}{\alpha} \varepsilon^{\frac{1}{p-1} - \gamma(\alpha+\beta+1)} = \frac{\alpha+\beta}{\alpha}(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)},
\end{equation*}
where we made use of the fact that $\alpha+1 = \frac{1}{p-1}$. We see that the first condition we want to impose is
\begin{equation}\label{e:condition_gamma_1}
    \fbox{\qquad\qquad\qquad$\displaystyle 0 < \gamma < \frac{\alpha+1}{\alpha+1+\beta}$\qquad\qquad\qquad.}
\end{equation}
As long as \eqref{e:condition_gamma_1} holds then
\begin{equation}\label{e:bddp_sigmaq_sigma}
    |\zeta_\sigma|\leq \mathfrak{C}_\alpha \qquad\text{where}\qquad \mathfrak{C}_\alpha = \frac{\alpha+\beta}{\alpha}(\alpha+1)^{\alpha+1}.
\end{equation}
\paragraph{\textcolor{blue}{\textbf{Step 6.}}} Recall $|\nabla d(x_\sigma)| = 1$, we have
\begin{align}
    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq \underbrace{\left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma}\right|^p}_{|\xi_\sigma|^p} - \underbrace{ \left|\frac{2\mathfrak{C}(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\nabla d(x_\sigma )\right|^p}_{|\xi_\sigma+\zeta_\sigma|^p} \nonumber\\
    &+ \underbrace{f(y_\sigma) - f(x_\sigma)}_{\mathfrak{F}|x_\sigma - y_\sigma|} + \varepsilon\left(\frac{2n}{\sigma} + \underbrace{\frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)}{d(x_\sigma)^{\alpha+\beta+2}}}_{\frac{C_\varepsilon (\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta + 1}}.\frac{\alpha+\beta+1}{d(x_\sigma)}}-\underbrace{\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)}_{\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}.\Delta d(x_\sigma)}\right)\nonumber\\
    &\leq |\xi_\sigma|^p - |\xi_\sigma+\zeta_\sigma|^p + \mathfrak{F}\sigma + \frac{2n\varepsilon}{\sigma} + (\alpha+\beta+1)|\zeta_\sigma|\frac{\varepsilon}{\sigma} + K|\zeta_\sigma|\varepsilon \label{e:est3}
\end{align}
where we recall that $K = \max_{x\in \overline{\Omega}}\Delta d(x)$. Let's recall a simple estimate, let $f(t) = (x+ty)^p$ then
\begin{align*}
    f(1) - f(0) = \int_ 0^1 f'(s)\;ds = p\int_0^1 (x+sy)^{p-1}y\;ds,
\end{align*}
therefore
\begin{align*}
    \left||x+y|^p - |x|^p \right| &\leq p \left(\int_0^1 |x+sy|^{p-1}ds\right)|y|\\
    &\leq p\left(\int_0^1\Big(|x|+s|y|\Big)^{p-1}\;ds\right)|y| \leq  p\Big(|x|+|y|\Big)^{p-1}|y|.
\end{align*}
Using this for $x = \xi_\sigma$ and $y = \zeta_\sigma$ we deduce that
\begin{align}
    \Big||\xi_\sigma+\zeta_\sigma|^p - |\xi|^p\Big| &\leq p\Big(|\xi_\sigma|+|\zeta_\sigma|\Big)^{p-1}|\zeta_\sigma|\nonumber\\
    &\leq p\left(2\mathfrak{C} + \frac{(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}\right)^{p-1}\frac{(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}\nonumber\\
    &\leq \underbrace{\left(p\big(2\mathfrak{C} + \mathfrak{C}_\alpha\big)^{p-1} \mathfrak{C}_\alpha \right)}_{\mathfrak{B}}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)} \label{e:est2}
\end{align}
where we make use of \eqref{e:bddp_sigmaq_sigma}.
\paragraph{\textcolor{blue}{\textbf{Step 7. Combining stuffs.}}} From \eqref{e:est2} and \eqref{e:est3} and $\sigma = \varepsilon^\gamma$ we deduce that
\begin{align*}
    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) &\leq   \mathfrak{B}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}+ \mathfrak{F}\varepsilon^\gamma + 2n \varepsilon^{1-\gamma}\\
    & + (\alpha+\beta + 1)\mathfrak{C}_\alpha \varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)} \varepsilon^{1-\gamma} + K\mathfrak{C}_\alpha\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)} \varepsilon.
\end{align*}
Let us denote
\begin{equation*}
    \mathfrak{X}:= \max\Big\lbrace \mathfrak{B}, \mathfrak{F},2n, (\alpha+\beta+1)\mathfrak{C}_\alpha, K\mathfrak{C}_\alpha \Big\rbrace
\end{equation*}
then
\begin{equation*}
    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq \mathfrak{X}\Big(\varepsilon^{\alpha+1-\gamma(\alpha+1+\beta)}+\varepsilon^\gamma+\varepsilon^{1-\gamma} + \varepsilon^{\alpha+2-\gamma(\alpha+2+\beta)}+\varepsilon^{\alpha+2-\gamma(\alpha+1+\beta)}\Big).
\end{equation*}
Take $\gamma = \frac{1}{2}$ to balance $\varepsilon^\gamma \approx \varepsilon^{1-\gamma}$ (\textcolor{blue}{which normally gives the rate $\sqrt{\varepsilon}$ for zero Dirichlet boundary problem}), we have
\begin{equation*}
    \begin{cases}
    \alpha+1 - \frac{1}{2}(\alpha+1+\beta) > \frac{1}{2}\vspace{3pt}\\
    \alpha+2 - \frac{1}{2}(\alpha+2+\beta) > \frac{1}{2}\vspace{3pt}\\
    \alpha+2 - \frac{1}{2}(\alpha+1+\beta) > \frac{1}{2}
    \end{cases} \qquad\Longleftrightarrow\qquad \begin{cases}
    \alpha+1-\beta > 1\\
    \alpha+2-\beta > 1\\
    \alpha+3-\beta > 1
    \end{cases}
\end{equation*}
which is always correct as long as $0 < \beta < \alpha$. We note that as $1<p<2$, we have $\alpha\in (0,\infty)$ and therefore such a choice of $\beta$ is always possible. We conclude that
\begin{equation}\label{e:crucial}
    \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq \mathfrak{X}\varepsilon^\frac{1}{2}
\end{equation}
where $\sigma = \varepsilon^\frac{1}{2}$. 
\paragraph{\textcolor{blue}{\textbf{Step 8. Deriving the conclusion}.}} Using $\Phi^\sigma(x_\sigma,y_\sigma)\geq \Phi^\sigma(x,x)$ for \textcolor{red}{all} $x\in \overline{\Omega}_\delta =  \overline{\Omega}_{2\sigma}$, we have
\begin{equation*}
    \lambda u^\varepsilon(x) - \lambda u_\delta(x) - \frac{C_\varepsilon}{d(x)^{\alpha+\beta}} \leq \Phi^\sigma(x_\sigma,y_\sigma) \leq \lambda u^\varepsilon(x_\sigma) - \lambda u_\delta(y_\sigma) \leq \mathfrak{X}\varepsilon^\frac{1}{2}.
\end{equation*}
Using $d(x)\geq 2\sigma = 2\varepsilon^{\frac{1}{2}}$ we deduce that
\begin{equation}\label{e:almost}
    \lambda u^\varepsilon(x) - \lambda u_\delta(x) \leq \mathfrak{X}\varepsilon^\frac{1}{2} + \frac{(\alpha+1)^{\alpha+1}}{2^{\alpha+\beta}\alpha}\varepsilon^{\alpha+1 - \frac{\alpha+\beta}{2}} \leq \tilde{\mathfrak{X}}\varepsilon^\frac{1}{2} \qquad \text{for all}\;x\in \overline{\Omega}_{2\sigma}
\end{equation}
where (we see that $\alpha+1 - \frac{\alpha+\beta}{2} = 1+ \frac{\alpha-\beta}{2} > 1$)
\begin{equation*}
    \tilde{\mathfrak{X}} = \max \left\lbrace\mathfrak{X}, \frac{(\alpha+1)^{\alpha+1}}{2^{\alpha+\beta}\alpha} \right\rbrace.
\end{equation*}
Finally, in the case of the ball, $\Omega_\delta = (1-\delta)\Omega$, by \cite[Theorem 1.5]{kim_state-constraint_2020} we know that, optimally,
\begin{equation}\label{e:citepaper}
    0\leq \lambda u_\delta(x) - \lambda u^0(x)\leq C_H\delta \qquad\text{for all}\; x\in \overline{\Omega}_\delta.
\end{equation}
From \eqref{e:almost} and \eqref{e:citepaper} and $\delta =2\sigma= 2\varepsilon^\frac{1}{2}$, and $u^\varepsilon \geq u^0$ from Theorem \ref{thm:qual} we deduce that
\begin{align*}
    \fbox{ $\displaystyle 0 \leq \lambda u^\varepsilon(x) - \lambda u^0(x) \leq \left(\tilde{\mathfrak{X}} + 2C_H\right)\sqrt{\varepsilon} \qquad\text{for all}\; x\in \overline{\Omega}_{2\sqrt{\varepsilon}}$.}
\end{align*}
It appears that the boundary layer is the strip
\begin{equation*}
    \Gamma_\varepsilon = \{x\in \Omega: 0<\mathrm\dist(x,\partial\Omega)< 2\sqrt{\varepsilon}\}.
\end{equation*}
\color{blue}
